---
title: "Twitter Shiny"
author: "Seong Nam"
date: "1/26/2021"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library('rtweet') ; 
library('tidyverse') ; 
library('syuzhet') ;
library('emo') ; 
library('wordcloud') ; 
library('DT') ; 
##library('tidytext')
```
## Introduction

This R Markdown document is made interactive using Shiny to demonstrate my abilities to make interactive data visualizations.

```{r load data, include=FALSE}
tweets <- search_tweets(q = "#rstats", 
                        n = 16000,
                        include_rts = FALSE,
                        `-filter` = "replies") #%>%
  #mutate(favorite_count = as.numeric(favorite_count), 
         #retweet_count = as.numeric(retweet_count))
         
                        
user_timeline  <- get_timeline("RLadiesSeattle", n = 900)
```

## Twitter data {.tabset}

### Recent Rstats tweets

### Tweets from @RLadiesSeattle

```{r tweets, echo=FALSE}
inputPanel(
  selectInput("tweetlang", label = "Language of tweets:",
              choices = unique(tweets$lang), selected = "en", multiple = TRUE)
)

renderPlot({
  ts_plot(tweets %>% filter(lang %in% input$tweetlang) , by = "hours", col = "blue")  +
    labs(x = NULL, y = NULL,
       title = "Frequency of tweets from containing #Rstats",
       subtitle = paste0(format(min(tweets$created_at), "%d %B %Y"), " to ", format(max(tweets$created_at),"%d %B %Y")),
       caption = "Data collected from Twitter's REST API via rtweet") + 
    theme_minimal()
})

rendertable({
  tweets %>%
    filter(lang %in% input$tweeetlang) %>%
    select(screen_name,text,lang,favorite_count,retweet_count)
})
```

### Tweets from @RLadiesSeattle
The plots below show the top emojis used, a wordle of terms, and a time series of tweets by @RLadiesSeattle. 
The time series can be plotted with different sources to see when different devices were used to tweet.

#### Time series plot of tweets
```{r user, echo=FALSE}
inputpanel(
  selecinput("tweetsource", label = "Source of Tweets:",
             choices = unique(user_timeline$source), selected=unique(user_timeline$source), multiple = TRUE)
)
```